### 2019-02-19 sections/intuition.tex
use breakfast as reusable example

\begin{example}[Breakfast]

The following program shows the different collaboration operators in action.
The user has a choice whether they want tea or coffee.
They always get an egg.
The drink and the food are prepared in parallel.
When drink and food are prepared, the user can step to eating the result.

@@

\begin{example}[Twice]

A higher-order function which executes a given task twice.
\begin{TASK}
  let twice : Task $\tau$ -> Task $\tau$ = \t : Task $\tau$. t >>? \x . t
\end{TASK}
The task value of the first execution is ignored.

>>>>

\begin{example}[Breakfast]
\label{exm:breakfast}

The following program shows the different collaboration operators in action.
Users have a choice whether they want tea or coffee.
They always get an egg.
The drink and the food are prepared in parallel.
When drink and food are prepared, users can step to eating the result.

@@

\Cref{exm:breakfast} demonstrates how tasks can be parameterized by other tasks: makeBreakfast is a collaboration pattern that always works the same way, regardless of which food and drink are being prepared.
